\thetitle

### 2013-04-17 tfpie/tfpie.tex
up

@@

\subsection{ProfessorJ}

\cite{dvanhorn:Bloch2000Scheme}

\cite{dvanhorn:Gray2003ProfessorJ}

The noble goals of ProfJ:

\begin{itemize}
\item language levels
\item continuity in IDE from first semester
\end{itemize}

Many of the shortcomings of HtDC and ProfJ are ``day 1'' problems.
The transition is too abrupt and too large.

@@

\begin{itemize}
\item dead.
\item changes languages from first semester rather than adding new
  concept (causes students confusing deep issue (O.O. design) and
  shallow ones (Java-like syntax) and orthogonal issues (static type
  discipline).  (This also ultimately lead to the tool being abandoned
  as it was too difficult to maintain.)

@@

% \nocite{*}
\bibliographystyle{eptcs}
\bibliography{dvh-bibliography,local}
\end{document}

>>>>

\usepackage[numbers]{natbib}
\usepackage{xspace}

@@

\subsection{TeachScheme! and ProfessorJ}

The TeachScheme! project initially focused only on the first course,
with the second course typically taught in Java in
institution-specific ways. Subsequently, the pedagogical approach was
extended to Java, but without the tool support and textbook of the
first course.  An example of this approach is described by
\citet{dvanhorn:Bloch2000Scheme}, who presents the experience
integrating these courses at Adelphi.  He reports that ``many of
Java's concepts could be introduced more easily in a second course
than a first''.

With these lessons in mind, the TeachScheme! project set out to apply
the lessons of teaching languages and IDE support to Java, as well as
to present the approach to object-oriented programming in textbook
form. ProfessorJ~\cite{dvanhorn:Gray2003ProfessorJ} is the resulting
system, accompanying the draft textbook \emph{How to Design
  Classes}~\cite{local:htdc}.  In parallel to our course, Northeastern
teaches the remainder of its computer science majors following this
approach.

ProfessorJ and How to Design Classes maintain many of the excellent
ideas of the first course.  In particular, ProfessorJ brings language
levels to Java, in an attempt to smooth the transition for students
from the first course and provide more helpful feedback.  ProfessorJ
is also embedded in the DrRacket IDE, increasing familiarity for the
students and supporting tools such as an interactive read-eval-print
loop.

\def\htdp{\emph{How to Design Programs}\xspace}
\def\htdc{\emph{How to Design Classes}\xspace}
\def\profj{{ProfessorJ}\xspace}

However, the ``day 1'' transition from the student languages used with
\htdp to \profj is too abrupt and too large.
%
Most significantly, changing languages from the first semester
immediately rather than simply adding a new concept confuses too many
issues for students.  On the first day of a \htdc-based course,
students see object-orientation, a new programming paridigm; Java, a
new language with new syntax, and static types, a crucial but
orthogonal concept.

This also ultimately lead to the tool being abandoned
  as it was too difficult to maintain.)

@@

\begin{itemize}
\item dead.
\item

@@

% \nocite{*}
\bibliographystyle{plainnat}
\bibliography{dvh-bibliography,local}
\end{document}
